Delta Factor - A New Authorization Factor

### 2022-08-11 paper1.tex
pix->table, citation#s, spellchk ok okay

%---------------------------------------------------------------------------------------------------------------------
% Following exactly professor's Canvas example
\section{Abstract}
\setlength{\baselineskip}{1.5\baselineskip}
%This is modus operandi bc as the paper evolves, the abstract changes invariably
\noindent
Man\_In\_The\_Middle-ware, (MITM)[14][15][20] is a rapidly growing field of website spoofing that is a challenge for everyone, especially for MITM mitigation and deterrence  developers to keep up with. Many papers have been published that explain the nuances, methods and lengths that the attackers use for "personal gain". According to [1], fairly spectacular results in detecting a MITM attack has been shown. This was accomplished by the group gathering attack data, metrics of the attacks, and analysis for many months, to eventually develop a custom phishing toolkit they named "phoca". That said, the target of our research is two-fold. Firstly, we show improvement in the Stonybrook claim via our novel composite-type methodology using COTP[13].  Secondly, we claim and show that despite Stonybrook's claim, it is possible and provable that application level checks based on easily acccessible and well known network level features along with a secret, can indeed determine with fine granularity, a MITM or !MITM. Ie., an efficient and novel server authentication factor has been developed.

@@

Choosing a window that doesn't typically happen, and that is large enough that small differences don't end up in different timing windows is critical. This work uses a prime number of 7ms to generate windows. Although other primes could be used, 7ms was the sweet spot for this experiment. Note: a similar approach to generating windows in TOTP is done, a integer division is used to determine the window a particular latency belongs too. (See code for reference)

@@

Finally, another future work is potientialy repeatedly validating or checking factors periodically. TLS addresses forward secrecy through rekeying, and this happens to be part of the protocol. The same process could trigger a transparent COTP generation and exchange. This type of feature is already possible on the browser side, and could be implemented on the server side as well. In addition, a new shared secret could be generated and shared upon rekeying, forward authentication is allowed. Those with access to previous details would not have future authentication.

>>>>

%---------------------------------------------------------------------------------------------------------------------
% Following exactly professor's Canvas example
\section{Abstract}
\setlength{\baselineskip}{1.5\baselineskip}
%This is modus operandi bc as the paper evolves, the abstract changes invariably
\noindent
Man\_In\_The\_Middle-ware, (MITM)[14][15][20] is a rapidly growing field of website spoofing that is a challenge for everyone, especially for MITM mitigation and deterrence  developers to keep up with. Many papers have been published that explain the nuances, methods and lengths that the attackers use for "personal gain". According to [1], fairly spectacular results in detecting a MITM attack has been shown. This was accomplished by the group gathering attack data, metrics of the attacks, and analysis for many months, to eventually develop a custom phishing toolkit they named "phoca". That said, the target of our research is two-fold. Firstly, we show improvement in the Stonybrook claim via our novel composite-type methodology using COTP[13].  Secondly, we claim and show that despite Stonybrook's claim, it is possible and provable that application level checks based on easily accessible and well known network level features along with a secret, can indeed determine with fine granularity, a MITM or !MITM. Ie., an efficient and novel server authentication factor has been developed.

@@

Choosing a window that doesn't typically happen, and that is large enough that small differences don't end up in different timing windows is critical. This work uses a prime number of 7ms to generate windows. Although other primes could be used, 7ms was the sweet spot for this experiment. Note: a similar approach to generating windows in TOTP is done, an integer division is used to determine the window a particular latency belongs too. (See code for reference)

@@

Finally, another future work is potentially repeatedly validating or checking factors periodically. TLS addresses forward secrecy through rekeying, and this happens to be part of the protocol. The same process could trigger a transparent COTP generation and exchange. This type of feature is already possible on the browser side, and could be implemented on the server side as well. In addition, a new shared secret could be generated and shared upon rekeying, forward authentication is allowed. Those with access to previous details would not have future authentication.
